Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-09-04 draft.tex
revise lemma 4 for decisive war

Thus $\frac{-\nu}{1 -\de} > \frac{\lambda + \mu + \beta}{1 -\de}$ guarantees that player $c$ will always be willing to counter an investment by player $p$ toward achieving recognition, making $p$ unwilling to make that investment in the initial stage and making the response by player $c$ unnecessary. A slightly weaker version of this inequality is stated as condition 4 so that this deterrence dynamic is guaranteed to operate through the war lottery as well, as will be seen in Lemma 4. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 4} \\
The difference in continuation values from switching from the status quo to taking the war lottery for player $p$ is $\frac{\lambda p_1 + \alpha p_2 }{1 -\de} +R_p^{SQ} -R_p^{WAR}$. For player $c$ it is $\frac{\nu p_1 + \beta p_2}{1 -\de} + R_c^{SQ} -R_c^{WAR}$. As noted above, $R_c^{SQ} =0$. So $c$ is willing to invest up to $\frac{\nu p_1 + \beta p_2}{1 -\de}$ toward preventing fighting if this quantity is negative (leave the case where it is non-negative until later).

$p$ is willing to invest up to $\frac{\lambda p_1 + \alpha p_2 }{1 -\de} +R_p^{SQ}$ toward instigating fighting when this quantity is positive, and will not invest when the quantity is non-positive. Thus we must only examine the case where this quantity is positive.

We will again set $R_p^{SQ}$ at its largest value of $\frac{\mu + \beta}{1-\de}$ as this is most restrictive. In this only case of interest, we have $\frac{\alpha p_2 + \lambda p_1 + \mu + \beta}{1 - \de}> 0$. Note that the first term is negative while the rest are positive.

Multiplying Condition 3 by $-p_{2s}$, we have $-\beta \cdot p_{2s} \geq \alpha \cdot p_{2s}$. Using this with Condition 4, we have $- \nu p_{1s} - \beta p_{2s} \geq \alpha p_{2s} +\lambda p_{1s} + \mu + \beta> 0 \ \forall p_{1s},p_{2s}$ and therefore also
\[
  \textstyle -\left(\frac{\nu p_{1s} + \beta p_{2s}}{1 -\de}\right) \geq \frac{\alpha p_{2s}+ \lambda p_{1s} + \mu + \beta}{1 - \de}> 0 \ \forall p_{1s},p_{2s}
\]

>>>>

Thus $\frac{-\nu}{1 -\de} > \frac{\lambda + \mu + \beta}{1 -\de}$ guarantees that player $c$ will always be willing to counter an investment by player $p$ toward achieving recognition, making $p$ unwilling to make that investment in the initial stage and making the response by player $c$ unnecessary. A slightly weaker version of this inequality is stated as condition 4 so that this deterrence dynamic is guaranteed to operate through the war lottery as well, as will be seen in Lemma 4. \hfill $\blacksquare$
\\
\\
\noindent {\bf Proof of Lemma 4} \\
The difference in continuation values from switching from the status quo to taking the war lottery for player $p$ is $\frac{\lambda p_{1s} + \alpha (1-p_{1s})}{1 -\de} +R_p^{SQ} -R_p^{WAR}$. For player $c$ it is $\frac{\nu p_{1s} + \beta (1-p_{1s})}{1 -\de} + R_c^{SQ} -R_c^{WAR}$. As noted above, $R_c^{SQ} =0$. So $c$ is willing to invest up to $\frac{\nu p_{1s} + \beta (1-p_{1s})}{1 -\de}$ toward preventing fighting if this quantity is negative (leave the case where it is non-negative until later).

$p$ is willing to invest up to $\frac{\lambda p_{1s} + \alpha (1-p_{1s})}{1 -\de} +R_p^{SQ}$ toward instigating fighting when this quantity is positive, and will not invest when the quantity is non-positive. Thus we must only examine the case where this quantity is positive.

We will again set $R_p^{SQ}$ at its largest value of $\frac{\mu + \beta}{1-\de}$ as this is most restrictive. In this only case of interest, we have $\frac{\alpha (1-p_{1s}) + \lambda p_{1s} + \mu + \beta}{1 - \de}> 0$. Note that the first term is negative while the rest are positive.

Multiplying Condition 3 by $-(1-p_{1s})$, we have $-\beta \cdot (1-p_{1s}) \geq \alpha \cdot (1-p_{1s})$. Using this with Condition 4, we have $- \nu p_{1s} - \beta (1-p_{1s}) \geq \alpha (1-p_{1s}) +\lambda p_{1s} + \mu + \beta> 0 \ \forall p_{1s},p_{2s}$ and therefore also
\[
  \textstyle -\left(\frac{\nu p_{1s} + \beta (1-p_{1s})}{1 -\de}\right) \geq \frac{\alpha (1-p_{1s})+ \lambda p_{1s} + \mu + \beta}{1 - \de}> 0 \ \forall p_{1s},p_{2s}
\]
